---
title: "Analysis Script"
author: "Shaina Trevino"
date: "2023-02-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install and load pacman package
#install.packages("pacman", repos = "http://cran.us.r-project.org") - UNCOMMENT
library(pacman)

#install and load required packages
p_load(devtools, here, readxl, janitor, tidyverse, openxlsx, robumeta, metafor) 
p_load_gh("thdiakon/ccaR", "mcguinlu/robvis") #from github

```


## Import

Import primary study eligibility data from `Eligibility_Data.xlsx`
 * Eligibility_Decisions: One row per primary study, data for eligibility decisions and reasons for exclude, when applicable
 * Reports: One row per reference, data for multiple reports/citations of a single primary study, when applicable
 * Citation_Matrix: One row per primary study, data on primary study overlap (which primary studies were included in each review)

```{r import-pselig}
#set path to eligibility data
elig_path <-here("data", "Eligibility_Data.xlsx")

#Import eligibility_decisions sheet of excel file and delete summed rows (last 4 rows)  
ps_eligibility <- read_excel(elig_path, sheet = "Eligibility_Decisions") %>% 
  filter(row_number() <= n()-4) %>% 
  janitor::clean_names() #make column names lowercase

#import excel primary study reference sheet
ps_allreferences <- read_excel(elig_path, sheet = "Reports") 

#import excel citation matrix (with header to calculate # of included/eligible studies)
ps_cm <- read_excel(elig_path, sheet = "Citation_Matrix")

#import excel citation matrix sheet (without header to transpose for lists of included/eligible reviews)
citation_matrix <- read_excel(elig_path, sheet = "Citation_Matrix", col_names = FALSE)
```

Import reconciled, review-level data in `Depression_Overview_FileMaker_Data.xlsx`
* Reference Level: One row per reference ID screened, abstract and eligibility decisions
* Review Level: One row per full-text-eligible review ID, extracted data at the review level

```{r import-review}
#set path to descriptive data
fd_path <- here("data", "Depression_Overview_FileMaker_Data.xlsx")

#import review level data files
reference_level <- read_excel(fd_path, sheet = "reference_level",
                                      guess_max = 123456) 

review_level <- read_excel(fd_path, sheet = "review_level")

review_amstar <- read_excel(fd_path, sheet = "amstar") #review level quality assessment

review_robis <- read_excel(fd_path, sheet = "robis") #review level risk of bias

```

Import reconciled, primary study level data in `Depression_Overview_FileMaker_Data.xlsx`
* Study Level: One row per study ID (eligible primary studies), extracted data at the primary study level
* Group Level: One row per user-created group ID, extracted data at the group level
* Outcome Level: One row per user-created outcome ID, extracted data at the outcome level

```{r import-study}
#import primary study level data files
study_level <- read_excel(fd_path, sheet = "study_level")

study_irob <- read_excel(fd_path, sheet = "iROB") #study level risk of bias

study_crob <- read_excel(fd_path, sheet = "cROB") #study level risk of bias

study_robins <- read_excel(fd_path, sheet = "ROBINS-I") #study level risk of bias

group_level <- read_excel(fd_path, sheet = "group_level")

outcome_level <- read_excel(fd_path, sheet = "outcome_level") 

```


Import cleaned, meta-analysis data in `Depression_Overview_Meta_Analysis.xlsx`
* Each outcome of interest is in a separate tab
  * One row per group comparison and outcome combination (intervention + comparison + outcome), **effect size for meta-analyses**

```{r import-ma}
#set path to meta-analysis data
ma_path <- here("data", "Depression_Overview_Meta_Analysis.xlsx")

#import meta-analysis data files
depression_diagnosis <- read_excel(ma_path, sheet = "Depression Diagnosis")

depression_symptoms <- read_excel(ma_path, sheet = "Depression Symptoms")

anxiety_symptoms <- read_excel(ma_path, sheet = "Anxiety")
```

## Pre-processing

